### 2020-08-01 thesis/chap_2.tex
updates some discu

>>>>

% Summary of results
% First the workshop
Conducting participatory research in Monteregie led us to a better understanding of the obstacles and assets to connectivity conservation in the region. The predominance of the agricultural land cover and its implications for land use planning and the regional economy was revealed as the most important source of obstacles for the region’s conservation goals, but also as a source of opportunities to develop more biodiversity-friendly farming practices. The expansion of urban infrastructure ranked high in more forested regions of the landscape. A range of assets was identified in the region: the strong engagement of local actors in connectivity conservation was a key factor. Through a consensual mapping workshop, we also mapped consensual priority core areas and links, showing how participants think corridors should make the best use of linear strips of the remaining forest of the region. Specifically, this demonstrates that participants saw small patches as important for corridor design and perceived corridors as an important tool to conserve and restore the potential of fragmented patches. However, it also means that designing corridors in such a way might mean that an otherwise important patch could be ignored because its location does not fit a linear corridor design.

% Then scenarios
The integration of those results to the land use change model shows how qualitative priorities from a participatory process can be turned into model inputs, and how the results compare to the business as usual scenario. These results complement those of chapter 1 and show similar patterns with regards to species response. When only looking at mean flow values, species with linear and simple response are those who seem to depend on forest types that are only under threat by land use change. On the other hand, species dependent on forest types that are under threat both by land use change and climate change show a more complex response, with more variations in the final outcome (2100 horizon) of the scenarios.

% What are we extending
We extend on the work of \cite{albert_applying_2017}, which implemented a simple land use change model, but did not attempt to generate any alternative scenarios. In many ways, this work can be compared to recent work that looked at how connectivity could change under a range of scenarios. One example is \cite{rubio_sustaining_2012} who tested whether a network of forested patches resilient to different land use change scenarios, for a species of nuthatch. They found that although identifying such a network was possible, its effectiveness and efficiency was under threat under certain scenarios. Our results suggest that findings of that sort are likely to change when climate change is considered, if the species under study is dependent on sensitive forest types.

% What are the implications
The results of our simple scenarios have implications for connectivity conservation in the region. The reforestation scenario suggests that reforesting as much land as is urbanized is what is necessary to maintain mean current flow. But this is only one simple measure of connectivity, and therefore those results suggest that more work is needed to explore which metric would be most appropriate to look at in this context, and more importantly what land use practices (protection, reforestation, urban densification) would be enough to maintain this metric. In the light of the results from our workshop, it is clear that reforesting the same amount that we are urbanizing is likely to be undeniable, given the amount of agricultural loss it generates.

% Why this methodology facilitates further work
Our methodology would allow us to explore alternative scenarios with ease. We imagined simple scenarios and therefore served as an intermediary between the workshop output and the model inputs. However, given the flexibility of the STSIM land use change model framework, steps could be taken to reduce that distance between stakeholders outputs and model inputs. The interest of stakeholders in participating in our workshop demonstrates that local actors are longing for tools that allow them to close the loop between what they think should be done and what it would effectively mean for species on the ground, and to explore where and how much reforestation would provide the optimal corridor design. To make this a reality, we are missing some knowledge about specific parameters - for instance, what the ideal width of a corridor for a given species, or how much agricultural loss is acceptable to reforestation. But we are also missing specific tools, and this project demonstrates that it is now easier to get there. The STSIM framework has been used in a participatory setting before. For instance, in \cite{jarnevich_developing_2019}, STSIM was used to produce a model for invasive species spread and fire management, using expert knowledge collected in a participatory setting. The authors also highlight the value to be found in involving “end users” of model results (i.e. stakeholders) in the modelling process. There remains a lot of work to be done to put these analyses in the hands of stakeholders. Making the analysis open and the code reproducible is one step in this direction.

% What are the limitations 
Perhaps the most important limitation of this work is the fact that the strong consensus which was quickly built during the workshop is fragilized by the absence of some key stakeholders which, in spite of being invited, were not able to partake in the activity. This further illustrates the need for consensual mapping and the need for an iterative process with the goal to involve a larger diversity of stakeholders. Participatory research scholars often emphasize the importance for a diverse set of participants, representative of the different interests at play in the region [CITE]. We can argue that the lack of representatives from foresters and farmers is a severe limitation of this study.

Similar limitations to those raised in chapter 1 also apply []. Another critique could be made about the targeted reforestation scenario: due to the parameterization of the reforestation, it was easier for patches in the north of the region to grow into linear strips of corridors. This happened at a lower rate in the southern part of the region, due to the lack of the pre-existing patches of forest. Future scenarios will need to test if allowing for new patches to spawn on the map produces the same outputs - as long as this land use change trend is thought likely by stakeholders.
